\clearpage

\thispagestyle{empty}



\chapter[Appendix]{List of all Publications by the Candidate} 



Following is a list of all the publications by the candidate including those on and related to the work presented in the thesis. The
publications are arranged in chronological order and in four sections -- (i) journals, (ii)
conferences, and (iii) workshops/research colloquiums.

\if{0}
\section*{Book Chapter}
\begin{enumerate}

 \item S. Srinivasan, {\bf T. Chakraborty}, and S. Bhowmick. ``Identifying Base Clusters and Their Application to Maximizing
Modularity''. {\it Contemporary Mathematics. Graph partitioning and Graph Clustering. (D. A. Bader, H. Meyerhenke, P. Sanders and D. Wagner
eds.), AMS-DIMACS}, pp. 141-156, 2012.

\end{enumerate}
\fi


\section*{Journals}
\begin{enumerate}
\item  {\bf Sandipan Sikdar}, Matteo Marsili and Animesh Mukherjee. ``Unsupervised Ranking of Clustering Algorithms by INFOMAX''. (communicated to CACM)

\item  Marcin Bodych, Niloy Ganguly, Tyll Kruger, Animesh Mukherjee, Rainer Seigmund-Schultze and {\bf Sandipan Sikdar}. ``Threshold based epidemic dynamics in systems with memory'', {\em Europhysics Letters (EPL), 116.4(2017):48004}.

\item  {\bf Sandipan Sikdar}, Niloy Ganguly, Animesh Mukherjee. `` Time series analysis of temporal networks'', {\em  European Physics Journal B topical issue on  Temporal Network Theory and Applications (EPJB 2016), volume 89(1), 1-11, DOI: 10.1140/epjb/e2015-60654-7}.

\item  Tanmoy Chakraborty, {\bf Sandipan Sikdar}, Niloy Ganguly, Animesh Mukherjee. `` Citation Interactions among Computer Science Fields: A Quantitative Route to the Rise and Fall of Scientific Research'', {\em Social Network Analysis and Mining 
(SNAM 2014), Springer, 4:187, pp. 1-18, DOI 10.1007/s13278-014-0187-3}.

\end{enumerate}

\section*{Conferences}
\begin{enumerate}

\item  {\bf Sandipan Sikdar}, Tanmoy Chakraborty, Soumya Sarkar, Niloy Ganguly and Animesh Mukherjee. `` ComPAS: Community Preserving Sampling for Streaming Graphs''. (communicated)

\item  {\bf Sandipan Sikdar}, Nitesh Sekhar, Matteo Marsili, Niloy Ganguly and Animesh Mukherjee. `` On the effectiveness of multiple reviewers in a peer-review system: A case study of two high impact Physics journals''. (communicated)

\item  Soumya Sarkar, {\bf Sandipan Sikdar}, Animesh Mukherjee and Sanjukta Bhowmick. ``Using Core-Periphery Structure to Predict High Centrality Nodes in Time-Varying Networks''. (communicated)

\item  {\bf Sandipan Sikdar}, Matteo Marsili, Niloy Ganguly and Animesh Mukherjee. `` Influence of Reviewer Interaction Network on Long-term Citations: A Case Study of the Scientific Peer-Review System of the Journal of High Energy Physics'', 
  {\em IEEE/ACM Joint Conference on Digital Libraries (JCDL), Toronto, Canada, 2017}.
  
\item  {\bf Sandipan Sikdar}, Matteo Marsili, Niloy Ganguly and Animesh Mukherjee. `` Anomalies in the peer-review system: A case study of the journal of High Energy Physics'', {\em ACM International Conference on 
Information and Knowledgement Management (CIKM), Indianapolis, USA, 2016}.

\item  {\bf Sandipan Sikdar}, Abhijnan Chakraborty, Anshit Choudhury, Gourav Kumar, S. Kumar, Abhijeet Patil, Niloy Ganguly and Animesh Mukherjee. `` Identifying and Characterizing Sleeping Beauties on YouTube'', {\em ACM Conference on Computer-Supported Cooperative Work and Social Computing (CSCW) 2016, San Francisco Poster highlights}.
  
\end{enumerate}

\section*{Workshops/ Research Colloquium}
\begin{enumerate}

\item {\bf Sandipan Sikdar}. `` Significance of scientific peer-review system: A case study of the Journal of High Energy Physics''. {\em JCDL Doctoral Consortium 2017}.

\item {\bf Sandipan Sikdar}, Marcin Bodych, Rajib Ranjan Maity, Biswajit Paria, Niloy Ganguly, Tyll Kruger, Animesh Mukherjee. `` On segmented message broadcast 
   in dynamic networks'', {\em IEEE INFOCOM workshop (Netscicom), HongKong, 2015}.
   
\item  Tanmoy Chakraborty, {\bf Sandipan Sikdar}, Niloy Ganguly, Animesh Mukherjee, `` Shift of Research Focus in Computer Sciences over the Last Fifty Years: What Citation Analysis Reflects?'' {\em Poster 
in TechVista organized by Microsoft Research India, Coimbatore, Tamil Nadu, on January 24, 2013 (Awarded Honorable mention award)}.   

\end{enumerate}