
\noindent
I would like to take the opportunity to thank everybody who inspired me, helped me and contributed directly or indirectly in realizing this
thesis. I want to thank all my family members who continuously supported throughout my life. I like to thank my father who always remains a
great inspiration for me. I like to thank my mother, who was also my childhood teacher and always stands by me for continuous support. My
parents did a lot of hard work to support logistics for studies and always encouraged me in every decision. I like to specially thank my
uncle, aunt and my little cute brother for their continuous support.  

The other persons who made a huge contribution and without whom the thesis would not have been possible are my supervisors, Dr.
Animesh Mukherjee and Prof. Niloy Ganguly. The long discussions with them not only helped me in culminating the problems of this thesis, but
also helped me to understand the nuances of doing research. His constant support and encouragement during the entire tenure of my PhD
motivated me to work harder for this thesis. I would like to say thank for all their support from the core of my heart. I would also like
to thank Dr. Sanjukta Bhowmick (University of Nebraska, Omaha), one of my collaborators, who has not only helped me with technical guidance
on my research, but more importantly, has taught me several ways of becoming a better researcher. I am very
much thankful to all my co-authors who directly contributed in this thesis. I want to specially convey thank to Suhansanu Kumar and
Sandipan Sikdar who have
remained as good friends and coauthors in a large part of my thesis. I always consider myself fortunate to be a part of the Complex Network
Research Group which
includes several good friends and excellent researchers. I want to extend my gratitude towards all my {\em CNeRG} lab mates Dr. Rajib Maiti,
Dr. Saptarshi Ghosh, Dr. Rishiraj Saha Roy, Dr. Sudipta Saha, Kaustav Rudra, Parantapa Bhattacharya, Animesh Srivastava, Abir De, Sourav
Dandapat, Sankarshan
Mridha, Abhijnan Chakraborty, Madhumita Mallick, Souvik Sur, Suman Maity, Soumajit
Pramanik and Mayank Singh. Continuous discussion with my lab mates not only helped me to enrich my knowledge in diverse fields but also was
hugely refreshing.  I express my sincere gratitude to the faculty
members and staffs of the department. I would specially like to thank the members of my Doctoral Scrutiny Committee,  Prof. S. Sarkar, Dr.
P. Mitra, Prof. J. Mukherjee, Dr. A. Mukherjee, and our Head of the Department, Prof. R. Mall for their invaluable suggestions regarding the
thesis. I was supported by Google India PhD Fellowship Award. I am thankful to several organizations such as Google India, ACM IARCS, Yahoo
India and to the organizers of conferences such as ACM SIGKDD, ACM CODS, COMAD for financial assistance for attending the
conferences.

I like to thank all my teachers throughout my life. I like to specially thank Mr. Dipankar Sannigrahi and Mr. Asish Kar who 
provided a continuous encouragement and confidence.

 
Finally, I am grateful to God for his blessings and for giving me the strength to persevere throughout the long and arduous journey towards a Ph.D.






