
\noindent Sandipan Sikdar has received his B-Tech. degree in 2012 from Computer Science and Engineering department of Institute of Engineering and Management, Kolkata.  
  


\singlespace
\begin{center}
\vspace{0.3cm}
{\bfseries {\large Publications from the Thesis
}}
\vspace{0.3cm}
\end{center}

\begin{enumerate}
\item  Sandipan Sikdar, Tanmoy Chakraborty, Soumya Sarkar, Niloy Ganguly and Animesh Mukherjee. ``ComPAS: Community Preserving Sampling for Streaming Graphs''. (communicated)
%\item  Sandipan Sikdar, Matteo Marsili and Animesh Mukherjee. ``Unsupervised Ranking of Clustering Algorithms by INFOMAX''. (communicated)
\item  Sandipan Sikdar, Nitesh Sekhar, Matteo Marsili, Niloy Ganguly and Animesh Mukherjee. `` On the effectiveness of multiple reviewers in a peer-review system: A case study of two high impact Physics journals''. (communicated)
 \item  Sandipan Sikdar, Matteo Marsili, Niloy Ganguly and Animesh Mukherjee. `` Influence of Reviewer Interaction Network on Long-term Citations: A Case Study of the Scientific Peer-Review System of the Journal of High Energy Physics'', JCDL, Toronto, Canada, 2017.
   \item  Marcin Bodych, Niloy Ganguly, Tyll Kruger, Animesh Mukherjee, Rainer Seigmund-Schultze and Sandipan Sikdar. `` Threshold based epidemic dynamics in systems with memory'', Europhysics Letters, 116.4(2017):48004.
   \item  Sandipan Sikdar, Matteo Marsili, Niloy Ganguly and Animesh Mukherjee. `` Anomalies in the peer-review system: A case study of the journal of High Energy Physics'', CIKM, Indianapolis, USA, 2016, .
   \item  Sandipan Sikdar, Abhijnan Chakraborty, Anshit Choudhury, Gourav Kumar, S. Kumar, Abhijeet Patil, Niloy Ganguly and Animesh Mukherjee. `` Identifying and Characterizing Sleeping Beauties on YouTube'', CSCW 2016, San Francisco Poster highlights.
   \item  Sandipan Sikdar, Niloy Ganguly, Animesh Mukherjee. `` Time series analysis of temporal networks'',European Physics Journal B topical issue on  Temporal Network Theory and Applications (2016), volume 89(1), 1-11, DOI: 10.1140/epjb/e2015-60654-7. 
   \item  Sandipan Sikdar, Marcin Bodych, Rajib Ranjan Maity, Biswajit Paria, Niloy Ganguly, Tyll Kruger, Animesh Mukherjee. `` On segmented message broadcast 
   in dynamic networks'', IEEE INFOCOM workshop (Netscicom), HongKong, 2015.
 %  \item  Tanmoy Chakraborty, Sandipan Sikdar, Niloy Ganguly, Animesh Mukherjee. `` Citation Interactions among Computer Science Fields: A Quantitative Route to the Rise and Fall of Scientific Research'', Social Network Analysis and Mining (SNAM 2014), Springer, 4:187, pp. 1-18, DOI 10.1007/s13278-014-0187-3.
 %  \item  Tanmoy Chakraborty, Sandipan Sikdar, Vihar Tammana, Niloy Ganguly, Animesh Mukherjee. `` Computer Science Fields as Ground-truth Communities: Their Impact, Rise and Fall'', IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM), Niagara Falls, Canada, August 25-28, 2013.(Nominated for best paper)
\end{enumerate}

