\noindent
\section{Summary of this chapter}
\label{conclusion}

Our contributions in this chapter can be summarized as below:
\begin{itemize}

\item we provided a general framework to map temporal network of human contacts consisting of a series of graphlets equispaced in time into time series
and provide a detailed time domain and frequency domain analysis.

\item we re-established the presence of structural correlation in a temporal network of human face-to-face contact using a new metric which we call
neighborhood-overlap.

\item we further quantified the extent of this correlation using neighborhood-overlap and used it to identify the correct window size in our prediction framework.

\item we also provided an approach for predicting the properties of future network instances using time series as a proxy and showed that even though the 
precise network structure is not known at time step, one can estimate its properties.

\item finally, we provided a frequency domain analysis of temporal network and leveraged it to enhance the prediction accuracy.

\item as an application we showed how our framework could be used in devising better strategies for targeted network attacks.
 
 \end{itemize}
 
 In its current state our framework can predict the values of the network properties at a future time step but is unable to offer the exact network 
 structure at that time step. But our framework can have genuine contributions toward link prediction in temporal networks. Since we show that structural 
 correlation exists in these networks and we can also predict the network properties at these time steps as well, we can re-frame the link prediction problem 
 as a network at a time step which is obtained from the network at a previous time step with minimal changes made depending on the values of the properties. 


\medskip